Effects of Reynolds Number on the Performance and Near-Wake of a Vertical-Axis Cross-Flow Turbine

### 2015-04-17 paper.tex
Add to conclusions

If using scaled physical models to predict array performance, it is important to
keep all turbines in the linear regime to avoid exaggerated power deficiencies
for downstream turbines, despite similarities in wake characteristics

>>>>

If using scaled physical models to predict array performance, it is important to
keep all turbines in the linear regime to avoid exaggerated power deficiencies
for downstream turbines, despite similarities in wake characteristics. These
results also suggest that low Reynolds number physical model stydies of turbine
arrays may see exaggerated levels of wake recovery, leading to inadequate or
inappropriate spacing or layouts.
